Astronomical Image colorization and up-scaling with generative adversarial networks

### 2021-09-27 Research Paper/iclr2022/iclr2022_conference.tex

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%\usepackage{cite}
\usepackage[authoryear]{natbib}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{hyperref}
\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={red}}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{varwidth}
\usepackage{tikz}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\usetikzlibrary{chains, calc,fit}

\title{Astronomical Image colorization and up-scaling with generative adversarial networks\\
}

\author{\IEEEauthorblockN{Shreyas Kalvankar \IEEEauthorrefmark{1}}
\IEEEauthorblockA{\textit{Dept. of Computer Engineering} \\
\textit{K. K. Wagh Institute of Engineering Education and Research}\\
Nashik, India \\
shreyas.kalvankar@kkwagh.edu.in}
\and
\IEEEauthorblockN{Snehal Kamalapur\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\textit{Dept. of Computer Engineering} \\
\textit{K. K. Wagh Institute of Engineering Education and Research}\\
Nashik, India \\
smkamalapur@kkwagh.edu.in}
\and
\IEEEauthorblockN{Hrushikesh Pandit\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\textit{Dept. of Computer Engineering} \\
\textit{K. K. Wagh Institute of Engineering Education and Research}\\
Nashik, India \\
hrushikesh.pandit@kkwagh.edu.in}
\and
\IEEEauthorblockN{Pranav Parwate\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\textit{Dept. of Computer Engineering} \\
\textit{K. K. Wagh Institute of Engineering Education and Research}\\
Nashik, India \\
pranav.parwate@kkwagh.edu.in}
\and
\IEEEauthorblockN{Atharva Patil\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\textit{Dept. of Computer Engineering} \\
\textit{K. K. Wagh Institute of Engineering Education and Research}\\
Nashik, India \\
atharva.patil@kkwagh.edu.in}
}

@@

\begin{IEEEkeywords}
Neural Networks, Generative Models, Image Colorization, Image Super-resolution
\end{IEEEkeywords}

\section{Introduction}
The problem of colorization of gray scale images with an automated algorithm has been under much research within the machine learning and computer vision communities. Beyond simply being fascinating from an aesthetic and artificial intelligence perspective, such capability has broad practical applications. It is an area of research that possesses great potentials in applications: from black and white photo reconstruction, image augmentation, image enhancement to video restoration for improved interpretability.
Image downscaling is an innately lossy process. The principal objective of super resolution imaging is to reconstruct a low resolution image into a high resolution one based on a set of low-resolution images to rectify the limitations that existed while the procurement of the original low-resolution images. This is to insure better visualization and recognition for either scientific or non-scientific purposes. Even if an upscaling algorithm is particularly good, there will always be some data loss from high frequency due to a downscale-upscale function performed on the image. Ultimately, even the best upscaling algorithms are unable to effectively reconstruct data that does not exist. Conventional methods for image upscaling rely on low-information and a smooth interpolation between known pixels. Thes methods can effectively be treated as a convolution with a kernel which encodes no information about the original image. The problem, has one of it's solutions as and can be solved by using Generative Adversarial Networks (GANs) to hallucinate high frequency data in a super scaled image that does not exist in the smaller image. Even though they increase the resolution of an image, they do not achieve the desired clarity in the super-resolution task. By using the above mentioned method, not a perfect reconstruction can be obtained albeit instead a rather plausible guess can be made at what the lost data might be, constrained to reality by a loss function penalizing deviations from the ground truth image.\\
\begin{figure}[!htb]
	\centering
	\begin{subfigure}[t]{0.4\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/samples_main}
		\caption{Ground Truth}
		\label{fig: main_color_samples}
	\end{subfigure}
		\hspace{0.1 in}
	\begin{subfigure}[b]{0.4\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/samples_full-trained}
		\caption{ResNet18 Full trained L*a*b}
		\label{fig: resnet18_full}
	\end{subfigure}
	\caption{Results of fine-tuned ResNet18 in L*a*b colorspace compared with ground truth images}
\end{figure}

@@

\section{Literature Review}
\subsection{Image Colorization}
\textit{Hint Based Colorization}\\
\hspace*{0.25 in}\citet{levin2004colorization} proposed using colorization hints from the user in a quadratic cost function which imposed that neighboring pixels in space-time with similar intensities should have similar colours. This was a simple but effective method but only had hints which were provided in form of imprecise colored scribbles on the grayscale input image. But with no additional information about the image, the method was able to efficiently generate high quality colorizations. \cite{huang2005edge} addressed the color bleeding issue faced in this approach and solved it using adaptive edge detection. \cite{yatziv2006chrominance} used luminescence based weighting for hints to boost efficiency. \cite{qu2006manga} extended the original cost function to apply color continuity over similar textures along with intensities.\\ \\
\hspace*{0.1 in}\textit{Deep Colorization}\\
\hspace*{0.25 in}Owing to recent advances, the Convolutional Neural Networks are a de facto standard for solving image classification problems and their popularity continues to rise with continual improvements. CNNs are peculiar in their ability to learn and differentiate colors, patterns and shapes within an image and their ability to associate them with different classes.\\
\hspace*{0.25 in}\cite{cheng2016deep} proposed a per pixel training for neural networks using DAISY \citep{tola2008descriptor}, and semantic \citep{long2015semantic} features to predict the chrominance value for each pixel, that used bilateral filtering to smooth out accidental image artifacts. With a large enough dataset, this method proved to be superior to the example based techniques even with a simple Euclidean loss function against the ground truth values.\\
\hspace*{0.25 in}Finally, \cite{dahl2016automatic} successfully implemented a system to automatically colorize black \& white images using several ImageNet-trained layers from VGG-16 \citep{simonyan2015deep} and integrating them with auto-encoders that contained residual connections. These residual connections merged the outputs produced by the encoding VGG16 layers and the decoding portion of the network in the later stages. \cite{he2015deep} showed that deeper neural networks can be trained by reformulating layers to learn residual function with reference to layer inputs. Using this \textit{Residual Connections}, \cite{he2015deep} created the \textit{ResNets} that went as deep as 152 layers and won the 2015 ImageNet Challenge.\\ \\
\hspace*{0.1 in}\textit{Generative Adversarial Networks}\\
\hspace*{0.25 in}\cite{goodfellow2014generative} introduced the adversarial framework that provides an approach to training a neural network which uses the generative distribution of $p_g(x)$ over the input data $x$.\\
\hspace*{0.25 in}Since it's inception in 2015, many extended works of GAN have been proposed over years including DCGAN \citep{radford2016unsupervised}, Conditional-GAN \citep{mirza2014conditional}, iGAN \citep{zhu2018generative}, Pix2Pix \citep{isola2018imagetoimage}.\\
\hspace*{0.25 in}\cite{radford2016unsupervised} applied the adversarial framework for training convolutional neural networks as generative models for images, demonstrating the viability of \textit{deep convolutional generative adversarial networks}.\\
\hspace*{0.25 in}DCGAN is the standard architecture to generate images from random noise. Instead of generating images from random noise, Conditional-GAN \citep{mirza2014conditional} uses a condition to generate output image. For e.g. a grayscale image is the condition for colorization of image. Pix2Pix \citep{isola2018imagetoimage} is a Conditional-GAN with images as the conditions. The network can learn a mapping from input image to output image and also learn a separate loss function to train this mapping. Pix2Pix is considered to be the state of the art architecture for image-image translation problems like colorization.
\subsection{Image Upscaling}
\textit{Frequency-domain-based SR image approach}\\
\hspace*{0.25 in} \cite{tsai1984multiframe} proposed the frequency domain SR method, where SR computation was considered for the noise free low resolution images. They transformed the low resolution images into Discrete Fourier transform (DFT) and further combined it as per the relationship between the aliased DFT coefficient of the observed low resolution image and that of unknown high resolution image. Then the output is transformed back into the spatial domain where a higher resolution is now achieved.\\
\hspace*{0.25 in} While Frequency-domain-based SR extrapolates high frequeny information from the low resolution images and is thus useful, however they fall short in real world applications.\\ \\
\hspace*{0.1 in}\textit{The interpolation based SR image approach}\\
\hspace*{0.25 in} The interpolation-based SR approach constructs a high resolution image by casting all the low resolution images to the reference image and then combining all the information available from every image available.
The method consists of the following three stages
(i) the registration stage for aligning the low-resolution input images,
(ii) the interpolation stage for producing a higher-resolution image, and
(iii) the deblurring stage which enhances the
reconstructed high-resolution image produced in the step (ii).

However, as each low resolution image adds a few new details before finally deblurring them, this method cannot be used if only a single reference image is available.\\ \\
\hspace*{0.1 in}\textit{Regularization-based SR image approach}\\
\hspace*{0.25 in} Most known Bayesian-based SR approaches are maximum likelihood (ML) estimation approach  and maximum a posterior (MAP) estimation approach.\\
\hspace*{0.25 in}  While \cite{Brian1996ML} proposed the first ML estimation based SR approach with the aim to find the ML estimation of high resolution image, some proposed a MAP estimation approach. MAP SR tries to takes into consideration the prior image model to reflect the expectation of the unknown high resolution image.\\ \\
\hspace*{0.1 in}\textit{Super Resolution - Generative Adversarial Networks (SR-GAN)}\\
\hspace*{0.25 in} The Genrative Adversarial Network \citep{goodfellow2014generative}, has two neural networks, the Generator and the Discriminator. These networks compete with each other in a zero-sum game.
\cite{ledig2017photorealistic} introduced SRGAN in 2017, which used a SRResNet to upscale images with an upscaling factor of 4x. SRGAN is currently the state of the art on public benchmark datasets.

@@

\subsection{Image Color Space}
\hspace*{0.25 in}An RGB image is essentially a rank 3 tensor of height, width and color where the last axis contains the color data of our image. The data is represented in RGB color space which has 3 numbers for every pixel indicating the amount of \textit{Red, Green, and Blue} values the pixel has.
\begin{figure}[!htb]
\begin{center}
	\includegraphics[width=0.5\textwidth]{figures/rgb_colorspace}
	\caption{Reg, Green and Blue channels of an image (Main image by \href{https://unsplash.com/@aznbokchoy}{Lucas Benjamin})}
	\label{rgb_colorspace}
\end{center}
\end{figure}
In \textbf{L*a*b} color space, we have three numbers for each pixel but these numbers have different meanings.L, the first channel, has the \textbf{Lightness} of each pixel encoded and when we visualize this channel it appears as a black and white image.
\begin{figure}[!htb]
\begin{center}
	\includegraphics[width=0.5\textwidth]{figures/Lab_colorspace}
	\caption{Lightness, *a and *b channels of the L*a*b colorspace}
	\label{lab_colorspace}
\end{center}
\end{figure}
The \textbf{*a and *b} channels encode in them exactly how much \textbf{green-red} and \textbf{yellow-blue} each pixel is, respectively.
\cite{guadarrama2017pixcolor,isola2018imagetoimage} propose the use of L*a*b color space instead of RGB to train the models. Intuitively, to the train a model for colorization, a grayscale image should be fed to it and we hope that it colors it. In the L*a*b colorspace, the model is fed the L channel, which is essentially a grayscale image, and we perform computations to predict the other two channels (*a and *b). After the predictions, we concatenate the channels and get a colorful image. In case of RGB, there is a need to explicitly convert the three channels down to 1 to make it a grayscale image and then feed it to the network hoping that it predicts three numbers per pixel. This is an unstable task due to sheer increase in volume of combinations from two numbers to three.

We train models using both color spaces and compare their performance.
\subsection{Mathematical Model}
\subsubsection{Generative Adversarial Networks}
 A generative network, $G$, is supposed to learn the underlying distribution of a latent space, Y. Instead of visually assessing the quality of network outputs and judge how we can adapt the network to produce convincing results, we incorporate automatic tweaking during training by introducing a discriminative network $D$. The network D takes in both the fabricated outputs generated by G and real inputs from the underlying distribution Y. The network produces a probability of the image belonging to the real or fabricated space.
\begin{figure*}[!htb]
    \centering
    \input{figures/tex_files/gan_visualization.tex}
    \caption{Approach for image colorization using conditional GANs. A sample grayscale image is provided as an input to the generator and the generated image along with the ground truth is fed to the discriminator. The probability \textit{p} is the probability that the discriminator thinks the two images are similar.}
    \label{fig:gan_visualization}
\end{figure*}
  Let $x \in X$ be a low resolution or a grayscale image and $y \in Y$ be it's underlying distribution from the latent space Y. Generator $G$ takes in input $x$ and produces an output $\hat{y}$. We define the mapping $x \rightarrow \hat{y}$ in the following manner:
  $$G(x) = \hat{y}$$

@@

\subsection{Transferred learning and model tweaking}
\hspace*{0.25 in}\cite{isola2018imagetoimage} proposed a general solution to many image-to-image translation tasks. We propose a similar methodology as proposed in the paper with a few minor tweaks, so as to significantly reduce the amount of training data needed and minimize the training time to achieve similar results. Initially, we propose the use of a U-net for the generator. A pre-trained ResNet-18 network was used as the \textit{encoder} for the U-net with half of it's layers clipped off so as to get feature abstractions of the intermediate layers. \cite{ledig2017photorealistic} showed that training the generator separately in a supervised, deterministic manner helps it generalize the mapping from the input space to outputs. The idea solves the problem of \textit{"The blind leading the blind"} that is persistent in most image-to-image translation tasks to date. \\
\hspace*{0.25 in}We pre-train our generator independently using the imagenet weights over the Common Objects in Context (COCO) dataset. Unlike adversarial training, this phase was supervised and the loss function used was \textit{mean absolute error} or the \textit{L1 Norm} from the target image. Though trained deterministically,the problem of rectifying incorrect predictions still persists due to constraints over the convergence of loss metric. To combat this, this trained generator was trained once again in an adversarial fashion to help generalize it further. We hypothesize that re-training in an adversarial fashion will further rectify the subtle color differences that \textit{mae} couldn't solve.\\
\hspace*{0.25 in}A pre-trained ResNet-50 with imagenet weights was used as the discriminator with last few layers clipped off. The discriminative network used is something called a "Patch Discriminator" proposed by \cite{isola2018imagetoimage}. In a \textit{vanilla} discriminator proposed by \cite{goodfellow2014generative}, the network produces a scalar output, representing the probability that the data $x$ belongs to the input distribution and not the generator distribution $p_g$. \cite{isola2018imagetoimage} proposed a modification to the discriminative network so as to produce, instead of a single scalar, a vector of probabilities representing different localities of the input distribution (image) $x$. For instance, a discriminator producing a $50 \times 50$ vector represents the probabilities every receptive field that is covered by the output vector. Thus, we can localize the corrections in the image that the generator should make.\\
\hspace*{0.25 in}Finally, the trained generator and trained discriminator are fine-tune to fit on our data which is rather small in size compared to the previous datasets. These networks are trained in an adversarial fashion using the conditional GAN objective function \citep{isola2018imagetoimage} with some noise introduced as the L1 norm of generated image tensor to the target image tensor. The reason behind this is to train the generator using an adversarial component while trying to minimize the Manhattan distance between the generator output and target vector space.
\subsection{Experimental Setup}
\hspace*{0.25 in}We use a mini-batch gradient descent with a batch size of 10, 16 and 32 for different iterations. We use Adam optimizer with $\beta_1 = 0.5$ and $\beta_2 = 0.999$. The generator and discriminator has a learning rate of $2e-4$ which remains constant throughout the training. We train the model with different epochs ranging between 20,50 and 100, saving the best model weights determined by L1 norm between the output of the generator and the target image. We use early stopping with a patience value of 10. The image size is $64\times64$. Our implementation is using Python, numpy, Tensorflow and tf-keras. It takes about 24 hours to complete training over the COCO dataset and about 12 to 13 hours to fit the model on given astronomical data on a NVIDIA Tesla K80 GPU.

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{iclr2022_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
%\usepackage[authoryear]{natbib}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={red}} 
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{varwidth}
\usepackage{tikz}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\title{Astronomical Image colorization and up-scaling with generative adversarial networks}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
about author (webpage, alternative address)---\emph{not} for acknowledging
funding agencies.  Funding acknowledgements go at the end of the paper.} \\
Department of Computer Science\\
Cranberry-Lemon University\\
Pittsburgh, PA 15213, USA \\
\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
\And
Ji Q. Ren \& Yevgeny LeNet \\
Department of Computational Neuroscience \\
University of the Witwatersrand \\
Joburg, South Africa \\
\texttt{\{robot,net\}@wits.ac.za} \\
\AND
Coauthor \\
Affiliation \\
Address \\
\texttt{email}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}
\usetikzlibrary{chains, calc,fit}

@@

\section{Introduction}

The problem of colorization of gray scale images with an automated algorithm has been under much research within the machine learning and computer vision communities. Beyond simply being fascinating from an aesthetic and artificial intelligence perspective, such capability has broad practical applications. It is an area of research that possesses great potentials in applications: from black and white photo reconstruction, image augmentation, image enhancement to video restoration for improved interpretability. 
    Image downscaling is an innately lossy process. The principal objective of super resolution imaging is to reconstruct a low resolution image into a high resolution one based on a set of low-resolution images to rectify the limitations that existed while the procurement of the original low-resolution images. This is to insure better visualization and recognition for either scientific or non-scientific purposes. Even if an upscaling algorithm is particularly good, there will always be some data loss from high frequency due to a downscale-upscale function performed on the image. Ultimately, even the best upscaling algorithms are unable to effectively reconstruct data that does not exist. Conventional methods for image upscaling rely on low-information and a smooth interpolation between known pixels. Thes methods can effectively be treated as a convolution with a kernel which encodes no information about the original image. The problem, has one of it's solutions as and can be solved by using Generative Adversarial Networks (GANs) to hallucinate high frequency data in a super scaled image that does not exist in the smaller image. Even though they increase the resolution of an image, they do not achieve the desired clarity in the super-resolution task. By using the above mentioned method, not a perfect reconstruction can be obtained albeit instead a rather plausible guess can be made at what the lost data might be, constrained to reality by a loss function penalizing deviations from the ground truth image.\\ 
    \begin{figure}[!htb]
    	\centering
    	\begin{subfigure}[b]{0.4\textwidth}
    		\centering
    		\includegraphics[width=\textwidth]{figures/samples_main}
    		\caption{Ground Truth}
    		\label{fig: main_color_samples}
    	\end{subfigure}
    		\hspace{0.1 in}
    	\begin{subfigure}[b]{0.4\textwidth}
    		\centering
    		\includegraphics[width=\textwidth]{figures/samples_full-trained}
    		\caption{ResNet18 Full trained L*a*b}
    		\label{fig: resnet18_full}
    	\end{subfigure}
    	\caption{Results of fine-tuned ResNet18 in L*a*b colorspace compared with ground truth images}
    \end{figure}

@@

\section{Literature Review}
\subsection{Image Colorization}
\subsubsection{Hint Based Colorization}
\hspace*{0.25 in}\citet{levin2004colorization} proposed using colorization hints from the user in a quadratic cost function which imposed that neighboring pixels in space-time with similar intensities should have similar colours. This was a simple but effective method but only had hints which were provided in form of imprecise colored scribbles on the grayscale input image. But with no additional information about the image, the method was able to efficiently generate high quality colorizations. \cite{huang2005edge} addressed the color bleeding issue faced in this approach and solved it using adaptive edge detection. \cite{yatziv2006chrominance} used luminescence based weighting for hints to boost efficiency. \cite{qu2006manga} extended the original cost function to apply color continuity over similar textures along with intensities.

\subsubsection{Deep Colorization}
\hspace*{0.25 in}Owing to recent advances, the Convolutional Neural Networks are a de facto standard for solving image classification problems and their popularity continues to rise with continual improvements. CNNs are peculiar in their ability to learn and differentiate colors, patterns and shapes within an image and their ability to associate them with different classes.\\
    \hspace*{0.25 in}\cite{cheng2016deep} proposed a per pixel training for neural networks using DAISY \citep{tola2008descriptor}, and semantic \citep{long2015semantic} features to predict the chrominance value for each pixel, that used bilateral filtering to smooth out accidental image artifacts. With a large enough dataset, this method proved to be superior to the example based techniques even with a simple Euclidean loss function against the ground truth values.\\
\hspace*{0.25 in}Finally, \cite{dahl2016automatic} successfully implemented a system to automatically colorize black \& white images using several ImageNet-trained layers from VGG-16 \citep{simonyan2015deep} and integrating them with auto-encoders that contained residual connections. These residual connections merged the outputs produced by the encoding VGG16 layers and the decoding portion of the network in the later stages. \cite{he2015deep} showed that deeper neural networks can be trained by reformulating layers to learn residual function with reference to layer inputs. Using this \textit{Residual Connections}, \cite{he2015deep} created the \textit{ResNets} that went as deep as 152 layers and won the 2015 ImageNet Challenge.\\

\subsubsection{Generative Adversarial Networks}
\hspace*{0.25 in}\cite{goodfellow2014generative} introduced the adversarial framework that provides an approach to training a neural network which uses the generative distribution of $p_g(x)$ over the input data $x$.\\
    \hspace*{0.25 in}Since it's inception in 2015, many extended works of GAN have been proposed over years including DCGAN \citep{radford2016unsupervised}, Conditional-GAN \citep{mirza2014conditional}, iGAN \citep{zhu2018generative}, Pix2Pix \citep{isola2018imagetoimage}.\\
    \hspace*{0.25 in}\cite{radford2016unsupervised} applied the adversarial framework for training convolutional neural networks as generative models for images, demonstrating the viability of \textit{deep convolutional generative adversarial networks}.\\
    \hspace*{0.25 in}DCGAN is the standard architecture to generate images from random noise. Instead of generating images from random noise, Conditional-GAN \citep{mirza2014conditional} uses a condition to generate output image. For e.g. a grayscale image is the condition for colorization of image. Pix2Pix \citep{isola2018imagetoimage} is a Conditional-GAN with images as the conditions. The network can learn a mapping from input image to output image and also learn a separate loss function to train this mapping. Pix2Pix is considered to be the state of the art architecture for image-image translation problems like colorization.

\subsection{Image Upscaling}
\subsubsection{Frequency-domain-based SR image approach}
\hspace*{0.25 in} \cite{tsai1984multiframe} proposed the frequency domain SR method, where SR computation was considered for the noise free low resolution images. They transformed the low resolution images into Discrete Fourier transform (DFT) and further combined it as per the relationship between the aliased DFT coefficient of the observed low resolution image and that of unknown high resolution image. Then the output is transformed back into the spatial domain where a higher resolution is now achieved.\\
    \hspace*{0.25 in} While Frequency-domain-based SR extrapolates high frequeny information from the low resolution images and is thus useful, however they fall short in real world applications.\\
\subsubsection{The interpolation based SR image approach}
\hspace*{0.25 in} The interpolation-based SR approach constructs a high resolution image by casting all the low resolution images to the reference image and then combining all the information available from every image available.
    The method consists of the following three stages
    (i) the registration stage for aligning the low-resolution input images,
    (ii) the interpolation stage for producing a higher-resolution image, and
    (iii) the deblurring stage which enhances the
    reconstructed high-resolution image produced in the step (ii).

    However, as each low resolution image adds a few new details before finally deblurring them, this method cannot be used if only a single reference image is available.\\

\subsubsection{Regularization-based SR image approach}
\hspace*{0.25 in} Most known Bayesian-based SR approaches are maximum likelihood (ML) estimation approach  and maximum a posterior (MAP) estimation approach.\\
    \hspace*{0.25 in}  While \cite{Brian1996ML} proposed the first ML estimation based SR approach with the aim to find the ML estimation of high resolution image, some proposed a MAP estimation approach. MAP SR tries to takes into consideration the prior image model to reflect the expectation of the unknown high resolution image.\\

\subsubsection{Super Resolution - Generative Adversarial Networks (SR-GAN)}
\hspace*{0.25 in} The Genrative Adversarial Network \citep{goodfellow2014generative}, has two neural networks, the Generator and the Discriminator. These networks compete with each other in a zero-sum game.
    \cite{ledig2017photorealistic} introduced SRGAN in 2017, which used a SRResNet to upscale images with an upscaling factor of 4x. SRGAN is currently the state of the art on public benchmark datasets.

@@

    \subsection{Image Color Space}
    \hspace*{0.25 in}An RGB image is essentially a rank 3 tensor of height, width and color where the last axis contains the color data of our image. The data is represented in RGB color space which has 3 numbers for every pixel indicating the amount of \textit{Red, Green, and Blue} values the pixel has.
    \begin{figure}[!htb]
    \begin{center}
    	\includegraphics[width=\textwidth]{figures/rgb_colorspace}
    	\caption{Reg, Green and Blue channels of an image (Main image by \href{https://unsplash.com/@aznbokchoy}{Lucas Benjamin})}
    	\label{rgb_colorspace}
    \end{center}
    \end{figure}
    In \textbf{L*a*b} color space, we have three numbers for each pixel but these numbers have different meanings.L, the first channel, has the \textbf{Lightness} of each pixel encoded and when we visualize this channel it appears as a black and white image. 
    \begin{figure}[!htb]
    \begin{center}
    	\includegraphics[width=\textwidth]{figures/Lab_colorspace}
    	\caption{Lightness, *a and *b channels of the L*a*b colorspace}
    	\label{lab_colorspace}
    \end{center}
    \end{figure}
    The \textbf{*a and *b} channels encode in them exactly how much \textbf{green-red} and \textbf{yellow-blue} each pixel is, respectively.
    \cite{guadarrama2017pixcolor,isola2018imagetoimage} propose the use of L*a*b color space instead of RGB to train the models. Intuitively, to the train a model for colorization, a grayscale image should be fed to it and we hope that it colors it. In the L*a*b colorspace, the model is fed the L channel, which is essentially a grayscale image, and we perform computations to predict the other two channels (*a and *b). After the predictions, we concatenate the channels and get a colorful image. In case of RGB, there is a need to explicitly convert the three channels down to 1 to make it a grayscale image and then feed it to the network hoping that it predicts three numbers per pixel. This is an unstable task due to sheer increase in volume of combinations from two numbers to three.

    We train models using both color spaces and compare their performance.
    \subsection{Mathematical Model}
    \subsubsection{Generative Adversarial Networks}
     A generative network, $G$, is supposed to learn the underlying distribution of a latent space, Y. Instead of visually assessing the quality of network outputs and judge how we can adapt the network to produce convincing results, we incorporate automatic tweaking during training by introducing a discriminative network $D$. The network D takes in both the fabricated outputs generated by G and real inputs from the underlying distribution Y. The network produces a probability of the image belonging to the real or fabricated space.
    \begin{figure}[!htb]
        \centering
        \resizebox{\textwidth}{!}{
        \input{figures/tex_files/gan_visualization.tex}}
        \caption{Approach for image colorization using conditional GANs. A sample grayscale image is provided as an input to the generator and the generated image along with the ground truth is fed to the discriminator. The probability \textit{p} is the probability that the discriminator thinks the two images are similar.}
        \label{fig:gan_visualization}
    \end{figure}
      Let $x \in X$ be a low resolution or a grayscale image and $y \in Y$ be it's underlying distribution from the latent space Y. Generator $G$ takes in input $x$ and produces an output $\hat{y}$. We define the mapping $x \rightarrow \hat{y}$ in the following manner:
      $$G(x) = \hat{y}$$

@@

    \subsection{Transferred learning and model tweaking}
    \hspace*{0.25 in}\cite{isola2018imagetoimage} proposed a general solution to many image-to-image translation tasks. We propose a similar methodology as proposed in the paper with a few minor tweaks, so as to significantly reduce the amount of training data needed and minimize the training time to achieve similar results. Initially, we propose the use of a U-net for the generator. A pre-trained ResNet-18 network was used as the \textit{encoder} for the U-net with half of it's layers clipped off so as to get feature abstractions of the intermediate layers. \cite{ledig2017photorealistic} showed that training the generator separately in a supervised, deterministic manner helps it generalize the mapping from the input space to outputs. The idea solves the problem of \textit{"The blind leading the blind"} that is persistent in most image-to-image translation tasks to date. \\
    \hspace*{0.25 in}We pre-train our generator independently using the imagenet weights over the Common Objects in Context (COCO) dataset. Unlike adversarial training, this phase was supervised and the loss function used was \textit{mean absolute error} or the \textit{L1 Norm} from the target image. Though trained deterministically,the problem of rectifying incorrect predictions still persists due to constraints over the convergence of loss metric. To combat this, this trained generator was trained once again in an adversarial fashion to help generalize it further. We hypothesize that re-training in an adversarial fashion will further rectify the subtle color differences that \textit{mae} couldn't solve.\\
    \hspace*{0.25 in}A pre-trained ResNet-50 with imagenet weights was used as the discriminator with last few layers clipped off. The discriminative network used is something called a "Patch Discriminator" proposed by \cite{isola2018imagetoimage}. In a \textit{vanilla} discriminator proposed by \cite{goodfellow2014generative}, the network produces a scalar output, representing the probability that the data $x$ belongs to the input distribution and not the generator distribution $p_g$. \cite{isola2018imagetoimage} proposed a modification to the discriminative network so as to produce, instead of a single scalar, a vector of probabilities representing different localities of the input distribution (image) $x$. For instance, a discriminator producing a $50 \times 50$ vector represents the probabilities every receptive field that is covered by the output vector. Thus, we can localize the corrections in the image that the generator should make.\\
    \hspace*{0.25 in}Finally, the trained generator and trained discriminator are fine-tune to fit on our data which is rather small in size compared to the previous datasets. These networks are trained in an adversarial fashion using the conditional GAN objective function \citep{isola2018imagetoimage} with some noise introduced as the L1 norm of generated image tensor to the target image tensor. The reason behind this is to train the generator using an adversarial component while trying to minimize the Manhattan distance between the generator output and target vector space.
    \subsection{Experimental Setup}
    \hspace*{0.25 in}We use a mini-batch gradient descent with a batch size of 10, 16 and 32 for different iterations. We use Adam optimizer with $\beta_1 = 0.5$ and $\beta_2 = 0.999$. The generator and discriminator has a learning rate of $2e-4$ which remains constant throughout the training. We train the model with different epochs ranging between 20,50 and 100, saving the best model weights determined by L1 norm between the output of the generator and the target image. We use early stopping with a patience value of 10. The image size is $64\times64$. Our implementation is using Python, numpy, Tensorflow and tf-keras. It takes about 24 hours to complete training over the COCO dataset and about 12 to 13 hours to fit the model on given astronomical data on a NVIDIA Tesla K80 GPU.

\section{Results and Discussions}
    \hspace*{0.25 in}In the following section, we briefly compare and summarize the results of the implemented architectures and evaluate their performance. The evaluation is done qualitatively as well as quantitatively. We compare the performance of each model using L1 and L2 norm distance between the predictions and targets. Though unreliable, this method provides us with a somewhat decent ground to perform a comparative study and evaluate the reliability of such metrics on GAN evaluation compared to qualitative, visual evaluation. We also measure the performance of the GANs by using Fréchet inception distance (FID) as an attempt to quantify how close the produced images are to the original ones.\\
    \hspace*{0.25 in}To evaluate the model performance by virtue of convergence of the objective function, we plot the generator loss throughout the training on two different networks.\\
    \begin{figure}[!htb]
    	\centering
    	\begin{subfigure}[b]{0.3\textwidth}
    		\centering
    		\includegraphics[width=\textwidth]{figures/resnet18_generator_loss}
    		\caption{ResNet18 U-net Generator}
    		\label{fig: resnet_loss}
    	\end{subfigure}
    		\hspace{0.1 in}
    	\begin{subfigure}[b]{0.3\textwidth}
    		\centering
    		\includegraphics[width=\textwidth]{figures/resnet18_discriminator_loss}
    		\caption{ResNet50 discriminator loss}
    		\label{fig: resnet50_disc_loss}
    	\end{subfigure}
    	\caption{Curve plots for ResNet18 U-net \& ResNet50 discriminator}
    	\label{fig: resnet18_curves}
    \end{figure}
    Figure \ref{fig: resnet_loss} and \ref{fig: resnet50_disc_loss} shows that the generator converges quite nicely. The discriminator on the other hand oscillates because of the convergence that the generator shows. GAN losses are pretty non-intuitive but we can draw some observations from the loss curves. It seems that the pattern of oscillation and convergence repeats when networks are trained in an adversarial fashion. It is observed that the ResNet U-net with a pre-trained ResNet-18 for its backbone converges decently in the beginning but later shows spikes when nearing the end of training loop. It seems that the loss convergence doesn't signify whether the model is predicting expected results. The loss function just converges to the minimum value that the cost function descends to, permitted by the learning rate. It would normally signify that the GAN has found some optimum point in the vector space that is at the lowest potential and cant decrease any further. It essentially means that the GAN has leaned enough. Due to the large number of dimensions, owing to the high amount of trainable variables, such combinations, where the function converges, can be huge in volume. Thus, these numbers don't provide any better understanding of the bias or variance the model is facing. Also, we discover that if the loss hasn't converged well, it doesn't necessarily mean that the model hasn't learned anything. On visual inspection, the generated results show similar results to the ground truth, even with high generator losses. This might be due to presence of a content loss parameter in the loss function where we try to minimize the function by  minimizing the L1 norm between the generator predictions and target.
